\Huge Handwritten digit recognition

### 2017-02-09 doc/Paper.tex
add interface ss to paper

\usepackage{amsmath}  % equations
\usepackage{cite}  % bibliograby
\usepackage{graphicx}  % images
\usepackage{pgfplots}  % plots
  \pgfplotsset{width=10cm,compat=1.9} % plots settings
  \usepgfplotslibrary{external}
  \tikzexternalize
\usepackage{todonotes}

@@

\newpage
\section{Graphical Interface}
The user is presented with a blank box in which to draw a digit to be recognized. Upon request, the prediction along with the model's confidence in it is displayed.

\missingfigure[figcolor=white]{GUI}

@@

\missingfigure[figcolor=white]{resizing example pdf}
The transformation can be computed by \textit{compacting} the columns:
$\sum_i Orig_i$ for column at index $\floor{\frac{i}{f}}$. Then for rows: $\sum_i Col_i$ for pixel at index $(i \bmod s) + \floor{\frac{i}{s \times f}}$. Where $Orig$ denotes the the original image $Col$ the column-wise averages.

>>>>

\usepackage{amsmath}  % equations
\usepackage{cite}  % bibliograby
\usepackage{graphicx}  % images
\usepackage{pgfplots}  % plots
  \pgfplotsset{width=10cm,compat=1.9} % plots settings
  \usepgfplotslibrary{external}
  \tikzexternalize
\usepackage{todonotes}
\usepackage{wrapfig}

@@

\newpage
\section{Graphical Interface}

The user is presented with a blank box in which to draw a digit to be recognized. Upon request, the prediction along with the model's confidence in it is displayed.

\begin{wrapfigure}{r}{0.6\textwidth}\centering
    \includegraphics[width=6cm]{images/gui.png}
\end{wrapfigure}

@@

\begin{center}
\includegraphics[width=\textwidth]{images/resize.png}
\end{center}

The transformation can be computed by \textit{compacting} the columns:
$\sum_i Orig_i$ for column at index $\floor{\frac{i}{f}}$. Then for rows: $\sum_i Col_i$ for pixel at index $(i \bmod s) + \floor{\frac{i}{s \times f}}$. Where $Orig$ denotes the the original image $Col$ the column-wise averages.
